Distributed Nonlinear Control Design using Separable Control Contraction Metrics

### 2017-05-31 R0V0.tex
Merge Ian's changes on preamble and biblio

\usepackage[natbib=true,backend=biber,style=ieee,
firstinits=true,doi=false,eprint=false,isbn=false,url=false,texencoding=utf8,bibencoding=utf8]{biblatex}
\addbibresource[location=remote]{https://www.dropbox.com/s/r00o9lw76cksxvj/Library.bib?dl=1} 
\AtBeginBibliography{\small}

@@

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{Humberto~Stein Shiromoto,~\IEEEmembership{Member,~IEEE,}
        Ian~R. Manchester,~\IEEEmembership{Member,~IEEE,}% <-this % stops a space
\thanks{Both authors are with the Department of Aerospace, Mechanical, and Mechatronic Engineering and The Australian Centre for Field Robotics. Address: The
Rose Street Building J04, The University of Sydney, NSW 2006, Australia. Corresponding author: {\tt h.stein.shiromoto@gmail.com}, {\tt orcid.org/0000-0002-0883-0231}}% <-this % stops a space
}

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\printbibliography

>>>>

%\usepackage[natbib=true,backend=biber,style=ieee,
%firstinits=true,doi=false,eprint=false,isbn=false,url=false,texencoding=utf8,bibencoding=utf8]{biblatex}
%\addbibresource[location=remote]{https://www.dropbox.com/s/r00o9lw76cksxvj/Library.bib?dl=1} 
%\AtBeginBibliography{\small}

@@

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Distributed Nonlinear Control Design using Separable Control Contraction Metrics}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{Humberto~Stein Shiromoto,~\IEEEmembership{Member,~IEEE,}
        Ian~R. Manchester,~\IEEEmembership{Member,~IEEE,}% <-this % stops a space
\thanks{Both authors are with the Australian Centre for Field Robotics, Department of Aerospace, Mechanical, and Mechatronic Engineering,
Rose Street Building J04, The University of Sydney, NSW 2006, Australia. Corresponding author: {\tt h.stein.shiromoto@gmail.com}, {\tt orcid.org/0000-0002-0883-0231}}% <-this % stops a space
}

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
%\printbibliography

\bibliographystyle{ieeetr}
\bibliography{Library,Distributed}
